% !TEX TS-program = xelatex
% !TEX encoding = UTF-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SIMPLE-RESUME-CV
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% INSTRUCTIONS FOR COMPILING THIS DOCUMENT ("CV.tex")
%% TeX ---(XeLaTeX)---> PDF:
%%
%% Method 1: Use latexmk for fully automated document generation:
%%   latexmk -xelatex "CV.tex"
%%   (add the -pvc switch to automatically recompile on changes)
%%
%% Method 2: Use XeLaTeX directly:
%%   xelatex "CV.tex"
%%   (run multiple times to resolve cross-references if needed)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \documentclass[a4paper,10pt,oneside]{article}
\documentclass[letterpaper,10pt,oneside]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% TYPESETTING OPTIONS.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\TypesetInNonStopMode}{1}
\newcommand{\TypesetInDraftMode}{0}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{CV-Preamble.tex}

% CV Info (to be customized).
\newcommand{\CVAuthor}{Anthony Li}
\newcommand{\CVTitle}{CV compiled on 310921 for Residency Application}
%\newcommand{\CVNote}{CV compiled on {\today} for Acme Corporation}
\newcommand{\CVWebpage}{http://llja0112.github.io}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
pdfpagemode={},
bookmarks=true,
unicode=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
colorlinks=true,
linkcolor=blue,
filecolor=blue,
urlcolor=blue,}

% Shorthand.
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\title{\CVAuthor}

\begin{subtitle}
%\href{https://www.google.com/maps/place/17+Prime+Avenue,+Springfield,+Pennsylvania+10111,+USA}
{Waterloo Street Block 262 \#12-219, Singapore, 180262}
\par
\href{mailto:anthony.li@mohh.com.sg}
{anthony.li@mohh.com.sg}
\,\SubBulletSymbol\,
+65 92385863\,
\href{\CVWebpage}
{\CVWebpage}
\end{subtitle}

\begin{body}

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\section
{Education}
{Education}
{PDF:Education}

{\textbf{M.D. Doctor of Medicine}, Duke NUS Medical School}
\hfill
\DatestampYMD{2015}{08}{01} -- \DatestampYMD{2019}{06}{01}

\GapNoBreak

\BigGap
{\textbf{B.Eng. Electrical Engineering}, National University of Singapore}
\hfill
\DatestampYMD{2009}{08}{01} --
\DatestampYMD{2013}{06}{01}

\GapNoBreak
\BulletItem
Awarded First Class Honors (GPA: 4.5/5)

\section
{Healthcare Experience}
{HealthcareExperience}
{PDF:HealthcareExperience}

{\textbf{Resident}, National University Health System, Regional Health System Office}
\hfill
\DatestampYMD{2023}{07}{01} --
Present
\BulletItem
Led the research on identifying biases in healthcare AI for minority populations e.g. transgender patients. Findings presented as clinical abstract and poster at annual USPATH 2023 conference.
\BulletItem
Led the exploration of new preventive medicine screening tools leveraging Large Language Models. Findings presented as clinical abstract and poster at Singapore's AI health summit 2023.  
\BulletItem
Developed AI models for Singapore's western population (n=1.1 million) diagnosing and predicting adverse outcomes for chronic diseases (e.g. Diabetes Mellitus, Hypertension, Dyslipidemia)
\BulletItem
Converted WPATH's SOC8 PDF copy to a mobile friendly digital web reference for clinicians and other users.

\BigGap
{\textbf{Resident}, Ministry of Health, Health Regulation Group}
\hfill
\DatestampYMD{2022}{07}{01} --
\DatestampYMD{2023}{06}{30}
\BulletItem
Worked on the following health policies: (1) Healthcare Financing for the Healthcare Services Act and, (2) Health data sharing and protection for the Health Information Bill.
\BulletItem
Worked with the Attorney General Chambers to draft legislation for the Health Information Bill.
\BulletItem
Worked with the Bioethics Committee Office to draft the ethical guidelines for Big Data, Artificial Intelligence and Human Nuclear Genome Editing in biomedical research.

\BigGap
{\textbf{Public Health Officer}, Tan Tock Seng Hospital, Clinical Epidemiology}
\hfill
\DatestampYMD{2021}{01}{01} --
\DatestampYMD{2022}{06}{30}
\BulletItem
Organised and led 5 COVID-19 vaccination awareness campaigns for 250 residents in Singapore's heartland communities.
\BulletItem
Supported Tan Tock Seng Hospital's COVID-19 Contact Tracing (CT) and Public Health (PH) operations over the COVID-19 Delta and Omicron waves.
\BulletItem
Operated the following key daily health surveillance systems: (1) Staff Acute Respiratory Infections. (2) Inpatient mortality. (3) Inpatient severe Dengue infections. (4) Inpatient and outpatient COVID-19 cases. (5) Emerging Infectious Disease horizon scanning.

\BigGap
{\textbf{Medical Officer}, Sengkang General Hospital (SKGH), General Medicine}
\hfill
\DatestampYMD{2020}{10}{01} --
\DatestampYMD{2021}{12}{31}
\BulletItem
SKGH isolation and high risk acute respiratory infection wards: Provided medical management of acute severe pnuemonia and COVID-19 patients.

\BigGap
{\textbf{Medical Officer}, Tan Tock Seng Hospital (TTSH), Infectious Disease Service}
\hfill
\DatestampYMD{2020}{07}{01} --
\DatestampYMD{2020}{09}{30}
\BulletItem
National Centre of Infectious Diseases (NCID) and Communicable Diseases Control (CDC) outbreak wards during the COVID-19 pandemic: Provided medical management for complex infectious diseases patients.

%\BigGap
%{\textbf{House Officer}, TTSH and SKGH}
%\hfill
%\DatestampYMD{2019}{07}{01} --
%\DatestampYMD{2020}{06}{30}
%\BulletItem
%Completed postgraduate year 1 postings in surgery and medicine. Attained full medical registration.


%\BigGap
%{\textbf{Research Medical Student}, National Heart Center Singapore}
%\hfill
%\DatestampYMD{2017}{09}{01} -- \DatestampYMD{2019}{07}{01} 
%\BulletItem 
%Performed research on predictive risk modelling for 3,885 Acute Coronary Syndrome (ACS) patients leveraging on ML methods such as XGBoost, MLP NN and LSTM RNN.
%\BulletItem
%Developed a novel method to improve ML model interpretability in ACS patients, thus identifying critical biomarkers (e.g. Creatinine, Total Cholesterol) for clinical intervention.

\section
{Other Professional Experience}
{WorkExperience}
{PDF:WorkExperience}

{\textbf{Software Engineer}, Experimental Systems and Technology Lab}
\hfill
\DatestampYMD{2014}{10}{01} --
\DatestampYMD{2015}{08}{01}
\BulletItem
Full stack development and deployment of applications for education under the Agile programming methodology. Technologies developed currently serves approximately 10,000 users.

\BigGap
{\textbf{Senior Officer}, A*STAR, Science and Engineering Research Council}
\hfill
\DatestampYMD{2013}{08}{01} --
\DatestampYMD{2014}{09}{31}
\BulletItem
Technology planning, grant administration and research management for Urban Systems Initiatives (S\$50 million grant), Satellite Initiatives and Infocomm Public Service Funding Research Projects.



%%% Research Activities %%%%
\section
{Research Publications}
{ResearchPublications}
{PDF:ResearchPublications}

\textbf{Publications}
\GapNoBreak
\definecolor{mygray}{gray}{0.4}

\begin{enumerate}
\item \underline{Anthony Li}, A. H. Aung, W. M. Kyaw, R. Khanna, W. Y. Lim, H. Ang, A. L. P. Chow \textcolor{mygray}{Harnessing a real-time location system for contact tracing in a busy emergency department}, \textit{Journal of Hospital Infection}[\href{https://www.journalofhospitalinfection.com/article/S0195-6701(23)00279-7/fulltext}{Paper link}]

\item \underline{Anthony Li}, M. L. Ong, C. W. Oei, W. X. Lian, H. P. Phua, H. L. Htun, W. Y. Lim, M. Motani \textcolor{mygray}{Unified Auto Clinical Scoring (Uni-ACS) with Interpretable ML models}, \textit{Proceedings of Machine Learning Research, Machine Learning for Healthcare Conference 2022 }[\href{https://static1.squarespace.com/static/59d5ac1780bd5ef9c396eda6/t/62e975060329a7015f4f6eab/1659467015391/15+MLHC2022_Uni_ACS_Camera_Ready.pdf}{Paper link}]


\item R. Khanna, H. L. Htun, \underline{Anthony Li}, H. L. Goh, W. M. Khyaw, H. Ang, B. Ang, A. Chow \textcolor{mygray}{Staff and patient surveillance in hospitals: Good sentinels for the emergence of the SARS-CoV-2 variants}, \textit{Journal of Infection }[\href{https://www.journalofinfection.com/article/S0163-4453(22)00411-X/fulltext}{Paper link}]


\item R. H. F. Lim, H. L. Htun, \underline{Anthony Li}, H. L. Goh, W. M. Khyaw, A. H. Aung, B. Ang, A. Chow \textcolor{mygray}{Fending off Delta – Hospital measures to reduce nosocomial transmission of COVID-19}, \textit{International Journal of Infectious Diseases }[\href{https://www.ijidonline.com/article/S1201-9712(22)00077-7/fulltext}{Paper link}]


\item A. Chow, H. L. Goh, W. M. Kyaw, \underline{Anthony Li}, R. H. F. Lim, B. Ang, \textcolor{mygray}{Rostered routine testing for severe acute respiratory coronavirus virus 2 (SARS-CoV-2) infection among healthcare personnel—Is there a role in a tertiary-care hospital with enhanced infection prevention and control measures and robust sickness-surveillance systems?}, \textit{SHEA Journal: Infection Control \& Hospital Epidemiology} [\href{https://www.cambridge.org/core/journals/infection-control-and-hospital-epidemiology/article/rostered-routine-testing-for-severe-acute-respiratory-coronavirus-virus-2-sarscov2-infection-among-healthcare-personnelis-there-a-role-in-a-tertiarycare-hospital-with-enhanced-infection-prevention-and-control-measures-and-robust-sicknesssurveillance-systems/30E175AEA1FBA0080DBB281D436D477B}{Paper link}]

\item D. W. Lim, H. L. Htun, Y. Wang, \underline{Anthony Li}, W. M. Kyaw, L. T. Lee, A. Chow, \textcolor{mygray}{Healthcare workers as 'canaries' for acute respiratory infections and pathogens during the COVID-19 pandemic}, \textit{The Journal of Hospital Infection} [\href{https://www.journalofhospitalinfection.com/article/S0195-6701(21)00140-7/fulltext}{Paper link}]

\item Sia S. X. Y., \underline{Anthony Li}, \textcolor{mygray}{Hierarchical Module Classification in Mixed Initiative Conversational Agent System}, \textit{27th ACM Conference on Information and Knowledge Management}
[\href{https://dl.acm.org/citation.cfm?id=3133185}{Paper link}]

\item Xiong W., \underline{Anthony Li}, Ong S.H., Sun Y. \textcolor{mygray}{Automatic 3D Prostate MRI Segmentation Using Graph Cuts and Level Sets}, \textit{Pacific-Rim Conference on Multimedia (PCM) 2013}
[\href{https://link.springer.com/chapter/10.1007/978-3-319-03731-8_20}{Paper link}]
\end{enumerate}

\textbf{Abstracts}
\GapNoBreak
\definecolor{mygray}{gray}{0.4}

\begin{enumerate}
\item \underline{Anthony Li}, S. X. Y. Sia, \textcolor{mygray}{Regulating LLMs in healthcare AI: An analysis of whether LLMs are sensitive to transphobic content}, \textit{US Professional Association of Transgender Health Conference 2023} [Oral Presentation / Poster]

\item \underline{Anthony Li}, T. Lim, J. J. Lee, E. Ng, Z. J. Ling \textcolor{mygray}{Application of LLMs for Preventive Healthcare Intervention Recommendations}, \textit{AI Health Summit 2023} [Oral Presentation / Poster]

\item \underline{Anthony Li}, W. Go, W. C. Chan, R. Chua \textcolor{mygray}{Guidance Tool for Development and Implementation of Safe Healthcare AI}, \textit{Machine Learning for Healthcare Conference 2023} [Oral Presentation / Poster]

\item \underline{Anthony Li}, Z. L. Huang, C. W. Oei, W. X. Lian, H. P. Phua, W. X. Ng, S. Y. Tay, \textcolor{mygray}{Learning from failure: Explaining clinical ML model prediction errors}, \textit{Machine Learning for Healthcare Conference 2022} [Oral Presentation / Poster]
[\href{https://static1.squarespace.com/static/59d5ac1780bd5ef9c396eda6/t/62e97c1b5754a426fa21d3bf/1659468827549/16+MLHC_Explaining_ML_model_failures_v4.pdf}{Paper link}]

\item \underline{Anthony Li}, C. W. Oei, H. P. Phua, W. X. Lian, L. H. Htet, S. H. Phua, G. P. Tan, H. Y. Xu, W. Y. Lim, J. Abisheganadan, \textcolor{mygray}{Application of Uni-ACS to COPD for prediction of Frequent Readmissions}, \textit{Singapore Health and Biomedical Conference 2022} [Oral Presentation / Poster]

\item \underline{Anthony Li}, C. W. Oei, H. P. Phua, W. X. Lian, L. H. Htet, W. Y. Lim, \textcolor{mygray}{Application of Machine Learning to predict 1 year All Cause Mortality in Chronic Obstructive Pulmonary Disease}, \textit{Singapore Health and Biomedical Conference 2021} [Oral Presentation / Poster]

\item \underline{Anthony Li}, T. M. Ng, A. Chow, \textcolor{mygray}{Early identification of bacteremia and its predictors with high performing Artificial Intelligence models}, \textit{Singapore Health and Biomedical Conference 2021} [Abstract]

%\item \underline{Anthony Li}, AO. Sahlen, \textcolor{mygray}{Improving clinical interpretation of extreme gradient boosted ensemble tree models of cardiac data with high proportions of missingness}, \textit{Machine Learning for Healthcare 2018} [Oral Presentation / Poster] [\href{https://static1.squarespace.com/static/59d5ac1780bd5ef9c396eda6/t/5b737a45032be4fab007b259/1534294605515/Li_A}{Paper link}]

%\item \underline{Anthony Li}, AO. Sahlen, \textcolor{mygray}{Superior prediction of outcome in ischemic heart disease with machine learning than regression modelling: importance of missing values}, \textit{Singapore Cardiology Society 30th Annual Scientific Meeting}
%[Oral Presentation]

%\item \underline{Anthony Li}, Deshpande A., Sarraf-Yazdi S. \textcolor{mygray}{Making meaning out of disorienting dilemmas, assumptions and emotions: a prelude to reflective write-ups}, \textit{International Consortium of Longitudinal Integrated Clerkship 2017}
%[Oral Presentation]

%\item Koong H. N., Bang D., Fung F. Y., \underline{Anthony Li} \textcolor{mygray}{A replay of our tutorials: A connection back to the soul of medical education}, \textit{International Consortium of Longitudinal Integrated Clerkship 2017}
%[Conference Workshop]

\end{enumerate}


%%% ACADEMIC GRANTS %%%%
\section
{Research Grants}
{Grants}
{PDF:Grants}

\textbf{AM ETHOS Medical Student Fellowship Grant 2017},
\hfill\DatestampYMD{2017}{10}{01}
\GapNoBreak
\textit{Singhealth Duke-NUS Academic Medicine Center}
\GapNoBreak
\BulletItem
Awarded a \$10,000 grant to study application of machine learning algortihms to Acute Coronary Syndrome patient PCI and echocardiograph datasets to predict patient mortality and morbidity.
\GapNoBreak



%%% ACADEMIC AWARDS %%%%
\section
{Awards}
{Awards}
{PDF:Awards}

\definecolor{mygray}{gray}{0.3}
\textbf{Young Investigator Award in Clinical Research, Silver}, \textit{SHBC 2022}
\hfill\DatestampYMD{2022}{10}{12}
\GapNoBreak
\BulletItem
2nd out of 365 submissions. Awarded to top clinical researchers under 40 years old, at Singapore's National Healthcare Group's annual healthcare and biomedical congress. Cash prize of \$600.
\GapNoBreak
\medskip

\definecolor{mygray}{gray}{0.3}
\textbf{Young Investigator Award in Clinical Research, Merit}, \textit{SHBC 2021}
\hfill\DatestampYMD{2021}{10}{01}
\GapNoBreak
\BulletItem
Top 5 out of 633 submissions. Awarded to top clinical researchers under 40 years old, at Singapore's National Healthcare Group's annual healthcare and biomedical congress. 
\GapNoBreak
\medskip

\definecolor{mygray}{gray}{0.3}
\textbf{LEAP award}, \textit{Singhealth Duke-NUS Academic Medicine Center}
\hfill\DatestampYMD{2019}{07}{07}
\GapNoBreak
\BulletItem
Awarded to 3 out of 65 selected medical students who have gotten honours grade for their clinical research projects under the mentorship of a Singhealth Academic Clinical Program Mentor. Cash prize of \$3000.
\GapNoBreak
\medskip

\definecolor{mygray}{gray}{0.3}
\textbf{2nd place}, \textcolor{mygray}{NUS-NUHS-MIT Healthcare Datathon 2018}, \textit{NUHS, NUS and MIT}
\hfill\DatestampYMD{2018}{07}{07}
\GapNoBreak
\BulletItem
2nd out of 40 paticipating teams. Organised by NUHS to address current problems in healthcare with data analytics technologies. Leveraged on gradient boosted trees and neural networks to study risk of cardiovascular complications in 10,389 diabetic surgical patients.
\GapNoBreak
\medskip

%\textbf{Special prize}, \textcolor{mygray}{Grow Asia Hackathon 2018}, \textit{Unilever, Bayer, MUFG and EastVentures}
%\hfill\DatestampYMD{2018}{03}{15}
%\GapNoBreak
%\BulletItem
%Designed AI/ML smartphone application to solve traceability and sustainability in Indonesia’s \$12B smallholder oil palm industry.
%\GapNoBreak
%\medskip

%\textbf{3rd place}, \textcolor{mygray}{Analyticup 2017}, \textit{27th ACM CIKM}
%\hfill\DatestampYMD{2017}{11}{05}
%\GapNoBreak
%\BulletItem
%Developed an RNN-LSTM based times series risk prediction model for DHL’s temperature controlled supply chain for biomedical product shipments.
%\GapNoBreak
%\medskip

\textbf{1st place}, \textcolor{mygray}{Singhealth Hackathon 2017}, \textit{Singapore General Hospital}
\hfill\DatestampYMD{2017}{01}{22}
\BulletItem
1st out of 20 participating teams. Organised by Singapore General Hospital to gather professionals and medical students across various disciplines within Singhealth cluster for the purpose of developing new innovative ideas to improve current patient care systems. Developed CHIT, a mobile application for communication and task coordination.
\GapNoBreak
\medskip

%\textbf{MTI Borderless Award}, \textit{Ministry of Trade and Industry}
%\hfill
%\DatestampYMD{2014}{06}{01}
%\BulletItem
%Awarded for outstanding contribution to Urban Systems Initiative research on sensor networks.
%\GapNoBreak

\textbf{A*STAR Borderless Award}, \textit{Science and Engineering Research Council}
\hfill
\DatestampYMD{2014}{05}{01}
\BulletItem
As a research grant administrator, I was recognised for outstanding cross agency policy contribution to A*STAR's urban system's initiative and Data Analytics platform.
\GapNoBreak
\medskip

\textbf{Dean's List}, \textit{National University of Singapore}
\hfill
\DatestampYMD{2013}{07}{01}
\BulletItem
Awarded to top 5\% of engineering students in academic excellence in NUS Faculty of Engineering.
\GapNoBreak


\section
{Humanitarian Projects}
{Projects}
{PDF:Projects}

\textbf{Enabling Red Cross Youth leaders for future public and global health challenges,} Red Cross South East Asian Youth Network
\hfill
\DatestampYMD{2022}{07}{01} -- Present
\BulletItem Awarded 2500 Swiss Francs from the International Federation of Red Cross to start a public and global health humanitarian leadership training programme.
\BulletItem Programme objective: To equip 20-30 Red Cross youth leaders from the South East Asian region with essential skills to design, implement and evaluate disaster preparedness and response programmes, for public health emergencies.
\GapNoBreak
\medskip

\textbf{Project Dawn}, Red Cross Youth NUS Chapter
\hfill
\DatestampYMD{2011}{06}{01} -- Present
\BulletItem Project Dawn is an overseas community involvement programme led by the Red Cross Youth NUS Chapter. In collaboration with local non-governmental organisations and Red Cross in Cambodia, Project Dawn delivers water sanitation and health hygiene programmes in the rural areas of Cambodia.
\BulletItem Led a team from 2011 to 2013 for direct missions to the province of Prey Veng. In addition to support of aforementioned programmes, team also dug wells and built libraries for 120 orphans from the Cambodia genocide by the Khmer Rogue.
%\BulletItem Provided advice and participated in fundraising for future teams from 2013 to 2019 for additional missions to Cambodia. Unfortunately, missions stopped due to COVID-19 pandemic. In discussion with stakeholders to restart missions.

%\textbf{Coagulopathy and Acute Kidney Injury in patients with severe COVID-19 disease}
%\BulletItem Collaborators: A/Prof Ngiam Kee Yuan and Dr Bryce Tan from NUHS as part of 4CE consortium.
%\BulletItem Objective: To study the inpatient trend of coagulopathy and AKI in COVID-19 patients from 96 hospitals across 5 countries.
%\BulletItem Reference: International electronic health record-derived COVID-19 clinical course profiles: the 4CE consortium [\href{https://www.nature.com/articles/s41746-020-00308-0}{Paper Link}]
%\GapNoBreak




\section
{Leadership \& Volunteerism}
{Student Leadership}
{PDF:StudentLeadership}

\textbf{Student Member}, WPATH and USPATH
\hfill
\DatestampYMD{2023}{06}{01} -- Present
\GapNoBreak

\textbf{Advisor}, Red Cross Youth Leadership Advisory Panel
\hfill
\DatestampYMD{2021}{01}{01} -- Present
\GapNoBreak

\textbf{Teacher Advisor}, Red Cross Youth NUS Chapter
\hfill
\DatestampYMD{2014}{06}{01} -- Present
\GapNoBreak

\textbf{Standard and Psychological First Aid Volunteer}, Singapore Red Cross Society
\hfill
\DatestampYMD{2010}{01}{01} -- Present
\GapNoBreak

\textbf{President}, Duke NUS Medical Technologies Student Group
\hfill
\DatestampYMD{2017}{08}{01} -- \DatestampYMD{2018}{08}{01} 
\GapNoBreak

\textbf{Vice President}, Duke NUS Emergency Medicine Student Group
\hfill
\DatestampYMD{2017}{08}{01} -- \DatestampYMD{2018}{08}{01} 
\GapNoBreak

\textbf{College Representative}, Duke NUS Benjamin Sheares College
\hfill
\DatestampYMD{2017}{08}{01} -- \DatestampYMD{2019}{07}{01} 
\GapNoBreak

\textbf{Clinical Peer Tutor}, Longitudinal Integrated Clerkship
\hfill
\DatestampYMD{2017}{10}{01} -- \DatestampYMD{2018}{08}{01} 
\GapNoBreak

\textbf{Vice President}, Red Cross Youth NUS Chapter
\hfill
\DatestampYMD{2012}{06}{01} -- \DatestampYMD{2013}{06}{01} 
\GapNoBreak

\textbf{Head}, Red Cross Youth NUS Chapter Disaster Management Group
\hfill
\DatestampYMD{2011}{06}{01} -- \DatestampYMD{2012}{06}{01} 
\GapNoBreak

\textbf{Logistics Head}, Red Cross Youth NUS Chapter Project Rice and Project Dawn
\hfill
\DatestampYMD{2010}{06}{01} -- \DatestampYMD{2011}{06}{01} 
\GapNoBreak

%\textbf{Hierarchical Module Classification Visualization}
%\newline Admin page to visualize decision making process behind patient bot responses. [\href{https://github.com/llja0112/medbot-server-admin}{Project link}]
%\GapNoBreak

%\textbf{Reflections platform}
%\newline Platform for medical students to write and consolidate reflections. [\href{https://github.com/llja0112/reflections}{Project link}] [\href{http://reflective.me}{Website link}]
%\GapNoBreak

%\textbf{Clinical knowledge platform}
%\newline Clinical knowledge made accessible in the form of checklists and approaches. [\href{http:\\medbot.me}{Website link}]

% \textbf{Medical Knowledge Website Scraper}
% \newline Scrap websites for knowledge to build models for patient bots. [\href{https://github.com/llja0112/medbot-scraper}{Project link}]

%%% CERTIFICATIONS %%%
\section
{Certifications}
{Certifications}
{PDF:Certifications}

\textbf{\textit{WPATH Foundations in Transgender Health Course (2 days) }} WPATH GEI
\hfill
\DatestampYMD{2023}{8}{1}
\BulletItem
Foundations in Transgender Health is intended for healthcare professionals and is a two-day training course that focuses on the importance of an interdisciplinary care team approach and cross-specialty foundational knowledge.

\textbf{\textit{Singapore Field Epidemiology Training Programme (5 weeks)}} NUS SSHSPH 
\hfill
\DatestampYMD{2022}{8}{5}
\BulletItem
The Singapore Field Epidemiology Training Programme (S-FETP) is conducted by the Saw Swee Hock School of Public Health and the National Centre for Infectious Diseases, to train participants in field investigation practice for infectious disease epidemiology.

\textbf{\textit{Epidemiology in Public Health Practice Specialisation (20 weeks)}} Coursera/JHU 
\hfill
\DatestampYMD{2021}{10}{31}
\BulletItem
[\href{https://www.coursera.org/account/accomplishments/specialization/certificate/XXUFMKJB2PPP}{Certificate link}]

\textbf{\textit{Deep Learning Specialisation (16 weeks)}} Coursera/DeepLearning.AI 
\hfill
\DatestampYMD{2018}{06}{30}
\BulletItem
[\href{https://www.coursera.org/account/accomplishments/specialization/certificate/9ACYUUL2YYDD}{Certificate link}]

\textbf{\textit{Probabilistic Graphical Models Specialisation (15 weeks)}} Coursera/Stanford University 
\hfill
\DatestampYMD{2018}{12}{01}
\BulletItem
[\href{https://www.coursera.org/account/accomplishments/specialization/certificate/ANDVMH29QHC6}{Certificate link}]


\section
{Programming}
{Programming}
{PDF:Programming}
\textbf{Languages:} Python, R, C, C++, Ruby, Octave/Matlab, HTML5, Javascript, CSS, SQL

\textbf{Deep Learning Frameworks:}  PyTorch, Tensorflow, Keras

\textbf{Packages:} SKLearn, XGBoost, SHAP, MICE, Caret, Tidyr, EpiNow2

\textbf{Tools:} Git, Latex, RStudio, Docker, Google Analytics, Jupyter Notebook, Visual Code, Atom

\textbf{Frameworks:} Rails, Elasticsearch, Logstash, Kibana, JQuery, React, Flux
%\textbf{Third party:} Heroku, Amazon Web Services, Digital Ocean, Mailgun
%\GapNoBreak
%\section
%{Languages}
%{Languages}
%{PDF:Languages}
%English, Chinese: Expert business proficiency
\end{body}

%%%%%%%%%%%
% CV NOTE %
%%%%%%%%%%%

\label{LastPage}~
\end{document}
